The Concurrent Calculi Formalisation Benchmark\\{\normalsize(Talk Proposal)

### 2023-07-11 talk-proposal/talk-proposal.tex
Rename "extended abstract" to "talk proposal".

Papers in concurrency theory do often include mechanized proofs (e.g.~\cite{DBLP:conf/tacas/CastroFY20, DBLP:conf/pldi/Castro-Perez0GY21,lmcs:9985, DBLP:journals/jar/CruzFilipeMP23, Tirore:2023}), and sometimes even target formalisation techniques as their main subject (e.g.~\cite{DBLP:conf/tphol/Gay01, DBLP:journals/jar/BengtsonPW16, DBLP:conf/ppdp/Thiemann19, DBLP:conf/forte/ZalakainD21}). However, our experience is that choosing techniques and tools remains a challenge with few guidelines.
We propose a new collection of benchmark problems specifically designed to tackle the issues encountered when mechanizing message-passing concurrency using process calculi.
A goal of our collection of benchmark problems is to enable comparison between techniques and push for the development of guidelines and tutorials, and our challenge problems are a simple setting in which to demonstrate and compare techniques.
Another goal is to strengthen the culture of mechanization by rallying the community to collaborate on exploring and developing new tools and techniques.

>>>>

Papers in concurrency theory do often include mechanized proofs (e.g.~\cite{DBLP:conf/tacas/CastroFY20, DBLP:conf/pldi/Castro-Perez0GY21,lmcs:9985, DBLP:journals/jar/CruzFilipeMP23, Tirore:2023}), and others also directly discuss formalisation techniques (e.g.~\cite{DBLP:conf/tphol/Gay01, DBLP:journals/jar/BengtsonPW16, DBLP:conf/ppdp/Thiemann19, DBLP:conf/forte/ZalakainD21}). However, our experience is that choosing techniques and tools remains a challenge with few guidelines.
We propose a new collection of benchmark problems specifically designed to tackle the issues encountered when mechanizing message-passing concurrency using process calculi.
A goal of our collection of benchmark problems is to enable comparison between techniques and push for the development of guidelines and tutorials, and our challenge problems are a simple setting in which to demonstrate and compare techniques.
Another goal is to strengthen the culture of mechanization by rallying the community to collaborate on exploring and developing new tools and techniques.
